Enforced Invariant Confluence

### 2018-04-22 doc/paper/sections/evaluation.tex
Finished TPC section.

\textbf{TPC-C and Feral Concurrency Control.}

TODO

>>>>

\example[TPC-C]\examplelabel{TpccEval}
TPC-C is a ubiquitous OLTP database benchmark with a workload that models a
simple warehousing application~\cite{difallah2013oltp}. The TPC-C specification
outlines twelve ``consistency requirements'' (read invariants) that govern the
warehousing application. In~\cite{bailis2014coordination}, Bailis et al.\
categorize the invariants into one of three types:
\begin{enumerate}
  \item
    Three of the twelve invariants are foreign key constraints.  As discussed
    in \exampleref{ForeignKeysEval}, our decision procedures can automatically
    verify conditions under which foreign key constraints are
    invariant-confluent.

  \item
    \newcommand{\ttt}[1]{{\smaller \texttt{#1}}}
    Seven of the twelve invariants involve maintaining arithmetic relationships
    between relations. Our decision procedures can correctly identify these as
    invariant-confluent. Consider, for example, invariant 1 which dictates that
    a warehouse's year to date balance \ttt{W\_YTD} is equal to the sum of the
    district year to date balances \ttt{D\_YTD} of the twenty districts that
    are associated with the warehouse. The Payment transaction randomly selects
    a district and increments \ttt{W\_YTD} and \ttt{D\_YTD} by a randomly
    generated amount. We model this workload with a PN-Counter for \ttt{W\_YTD}
    and twenty PN-Counters for the twenty instances of \ttt{D\_YTD}. We applied
    Lucy to this workload, and it determined that the workload was
    invariant-confluent in less than a second.

  \item
    Two of the twelve invariants involve generating sequential and unique
    identifiers. This workload is \emph{not} invariant-confluent, but when the
    sequentiality requirement is dropped, it is invariant-confluent.
    Unfortunately, modelling unique key generation in our theoretical framework
    (and in our prototype implementation) is not possible because we have thus
    far tacitly assumed that transaction execution is deterministic. We leave a
    generalization of our theory to non-deterministic transactions for future
    work.
\end{enumerate}
